### 2025-09-25 paper/sec/related-work.tex
Related work tweaks.

\paragraph{Argument mining.}
For over fifteen years the field of NLP has been exploring the problem of argument mining, which involves
identifying argumentative structures in text, such as claims, premises, and conclusions, and mapping them to
formal representations~\citep{palau2009argumentation,lippi2015argument} . Early work in this area focused on
rule-based approaches, while more recent work has leveraged machine learning and deep learning techniques to
improve performance~\citep{stab2014identifying,stab2017parsing,eger2017neural}. The field has also emphasized
defining annotation schemes for the task, such as the Argumentative Zoning
framework~\citep{teufel2002summarizing,teufel2009towards}, as well as schemes more directly tailored to
argument mining~\citep{stab2014annotating}. The field has focused on various domains, starting from legal
texts~\citep{toulmin2003uses}, and has relied on online resources such as
Debatepedia~\citep{cabrio2013natural}. The community has also rapidly engaged with work that explores the use
of argument mining in scientific texts~\citep{liakata2012automatic,lauscher2018investigating} to better
understand the structure of scientific arguments and the relationships between different claims and evidence.
While the advent of LLMs has improved performance~\citep{gorur2025can,vrakatseli2025can}, argument mining
remains a challenging task, particularly when it comes to identifying implicit argumentative relations between
discourse units, and reasoning about relationships among different argumentative components, especially in
cross-domain settings where models struggle to generalise~\citep{gemechu2024aries}. While in our work we do
not directly perform traditional argument mining, this work similarly relies on the identification of claims
in text, which we evaluate following established practices in the field.

>>>>

\paragraph{Argument mining.}
\emph{Argument mining} is an area of NLP which involves identifying argumentative structures in text, such as
claims, premises, and conclusions, and mapping them to formal
representations~\citep{palau2009argumentation,lippi2015argument}. Early work focused on rule-based approaches,
while more recent work has leveraged machine learning and deep learning
techniques~\citep{stab2014identifying,stab2017parsing,eger2017neural}. The field has also emphasized defining
annotation schemes for the task, such as the Argumentative Zoning
framework~\citep{teufel2002summarizing,teufel2009towards}, as well as schemes more directly tailored to
argument mining~\citep{stab2014annotating}. The field has focused on various domains, starting from legal
texts~\citep{toulmin2003uses}, and has relied on online resources such as
Debatepedia~\citep{cabrio2013natural}. The community has also rapidly engaged with work that explores the use
of argument mining in scientific texts~\citep{liakata12,lauscher2018investigating} to better understand the
structure of scientific arguments and the relationships between different claims and evidence. While the
advent of LLMs has improved performance~\citep{gorur2025can,vrakatseli2025can}, argument mining remains a
challenging task, particularly when it comes to identifying implicit argumentative relations between discourse
units, and reasoning about relationships among different argumentative components, especially in cross-domain
settings where models struggle to generalise~\citep{gemechu2024aries}. While in our work we do not directly
perform traditional argument mining, this work similarly relies on the identification of claims in text, which
we evaluate following established practices in the field.
